Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-03-05 manuscript/manuscript.Rmd
updated figures

stats <- ddply(ipm_onestep, .(species, year), summarise,
               mean_resid = mean(resid),
               sd_resid = sd(resid),
               min_resid = min(resid),
               max_resid = max(resid))
stats$model <- rep("IPM", nrow(stats))
colnames(stats)[2] <- "simtype"
stats2 <- ddply(resDall, .(species, simtype), summarise,
               mean_resid = mean(resids),
               sd_resid = sd(resids),
               min_resid = min(resids),
               max_resid = max(resids))
stats2$model <- rep("QBM", nrow(stats2))
stats$simtype <- stats2$simtype
stats <- rbind(stats, stats2)
stats <- stats[,c(ncol(stats),1:(ncol(stats)-1))]
stats$simtype <- rep(c("Full", "Climate"),(nrow(stats)/2))
colnames(stats) <- c("Model", "Species", "Year Structure", "Mean", "SD", "Min", "Max")
print.xtable(xtable(stats, caption = "Table of residual summary statistics."),type="latex", comment=FALSE, include.rownames=FALSE)
```

>>>>

stats <- ddply(ipm_onestep, .(species, year), summarise,
               mean_resid = mean(abs(resid)),
               sd_resid = sd(resid),
               min_resid = min(resid),
               max_resid = max(resid))
stats$model <- rep("IPM", nrow(stats))
colnames(stats)[2] <- "simtype"
stats2 <- ddply(resDall, .(species, simtype), summarise,
               mean_resid = mean(abs(resids)),
               sd_resid = sd(resids),
               min_resid = min(resids),
               max_resid = max(resids))
stats2$model <- rep("QBM", nrow(stats2))
stats$simtype <- stats2$simtype
stats <- rbind(stats, stats2)
stats <- stats[,c(ncol(stats),1:(ncol(stats)-1))]
stats$simtype <- rep(c("Full", "Climate"),(nrow(stats)/2))
colnames(stats) <- c("Model", "Species", "Year Structure", "Mean", "SD", "Min", "Max")
print.xtable(xtable(stats, caption = "Table of residual summary statistics."),type="latex", comment=FALSE, include.rownames=FALSE)
```

### 2015-03-05 manuscript/manuscript.tex
updated figures

>>>>

\subsection{Tables}\label{tables}

\begin{table}[ht]
\centering
\begin{tabular}{lllrrrr}
  \hline
Model & Species & Year Structure & Mean & SD & Min & Max \\ 
  \hline
IPM & BOGR & Full & 3.42 & 5.78 & -46.52 & 43.05 \\ 
  IPM & BOGR & Climate & 5.77 & 11.40 & -230.10 & 47.81 \\ 
  IPM & HECO & Full & 0.56 & 0.95 & -10.99 & 4.33 \\ 
  IPM & HECO & Climate & 0.60 & 1.05 & -8.65 & 6.67 \\ 
  IPM & PASM & Full & 0.17 & 0.30 & -4.29 & 1.04 \\ 
  IPM & PASM & Climate & 0.14 & 0.20 & -2.04 & 0.99 \\ 
  IPM & POSE & Full & 0.91 & 1.65 & -30.73 & 7.34 \\ 
  IPM & POSE & Climate & 0.72 & 1.51 & -6.08 & 14.32 \\ 
  QBM & BOGR & Full & 6.80 & 12.45 & -81.48 & 52.88 \\ 
  QBM & BOGR & Climate & 7.69 & 13.61 & -94.71 & 54.33 \\ 
  QBM & HECO & Full & 0.94 & 2.28 & -68.53 & 7.84 \\ 
  QBM & HECO & Climate & 1.26 & 3.49 & -94.57 & 7.91 \\ 
  QBM & PASM & Full & 0.26 & 0.50 & -15.13 & 1.56 \\ 
  QBM & PASM & Climate & 0.27 & 0.53 & -9.69 & 1.67 \\ 
  QBM & POSE & Full & 0.86 & 2.07 & -58.34 & 13.97 \\ 
  QBM & POSE & Climate & 1.12 & 2.47 & -73.14 & 15.18 \\ 
   \hline
\end{tabular}
\caption{Table of residual summary statistics.} 
\end{table}

### 2015-03-05 manuscript/suppMat.Rmd
updated figures

```{r figure_S1, dependson="plot-options", fig.cap="The proportion of interannual variability in  vital rates explained by the climate covariates. The contribution for growth is defined as: (Climate model - Constant Model)/(Full model - Constant model). The contribution for survival and colonization, where we could not estimate a full model with year random effects at the quadrat level, is defined as: (Constant Model - Climate Model)/Constant Model.", fig.width=7, fig.height=3, cache=FALSE, results='hide'}
deviance <- data.frame(VitalRate = c("Growth", "Survival", "Colonization"),
                       ConstantModel = rep(NA,3),
                       ClimateModel = rep(NA,3),
                       FullModel = rep(NA,3),
                       ClimateContribution = rep(NA,3))
deviance$FullModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDeviance.csv")[,2],2)
deviance$ClimateModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDevianceCLIMATE.csv")[,2],2)
deviance$ConstantModel[1] <- round(read.csv("../montana/quadBM/vitalRateRegressions/growth/growthDevianceCONSTANT.csv")[,2],2)
deviance$ClimateContribution[1] <- with(deviance[1,], (ClimateModel-ConstantModel)/(FullModel-ConstantModel))
deviance$ClimateModel[2] <- round(read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalDeviance.csv")[,2],2)
deviance$ConstantModel[2] <- round(read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalDevianceCONSTANT.csv")[,2],2)
deviance$ClimateModel[3] <- round(read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationDeviance.csv")[,2],2)
deviance$ConstantModel[3] <- round(read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationDevianceCONSTANT.csv")[,2],2)
deviance$ClimateContribution[2:3] <- with(deviance[2:3,], (ConstantModel-ClimateModel)/(ConstantModel))

colnames(deviance) <- c("Vital Rate", "Constant model", "Climate model", "Full model", "Contribution of climate covariates")
library(ggplot2)
devGQ <- data.frame(VitalRate = c("Growth", "Survival", "Colonization"),
                       ConstantModel = rep(NA,3),
                       ClimateModel = rep(NA,3),
                       FullModel = rep(NA,3),
                       ClimateContribution = rep(NA,3))
devGQ$FullModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDeviance.csv")[,2],2)
devGQ$ClimateModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[1] <- round(read.csv("../montana/ipm/vitalRateRegs/growth/growthDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDeviance.csv")[,2],2)
devGQ$ClimateModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[2] <- round(read.csv("../montana/ipm/vitalRateRegs/survival/survivalDevianceCONSTANT.csv")[,2],2)
devGQ$FullModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDeviance.csv")[,2],2)
devGQ$ClimateModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCLIMATE.csv")[,2],2)
devGQ$ConstantModel[3] <- round(read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentDevianceCONSTANT.csv")[,2],2)
devGQ$ClimateContribution[1] <- with(devGQ[1,], (ClimateModel-ConstantModel)/(FullModel-ConstantModel))
devGQ$ClimateContribution[2] <- with(devGQ[2,], (ConstantModel-ClimateModel)/(ConstantModel))
devGQ$ClimateContribution[3] <- with(devGQ[3,], (ConstantModel-ClimateModel)/(ConstantModel))

devM <- devGQ[,c(1,5)]
devM$Level <- rep("Individual", 3)
tmpD <- deviance[,c(1,5)]
tmpD$Level <- rep("Quadrat", 3)
colnames(tmpD)[2] <- "value"
colnames(tmpD)[1] <- "VitalRate"
colnames(devM)[2] <- "value"
plotD <- rbind(tmpD, devM)
gClimCont1 <- ggplot(data=subset(plotD, Level=="Individual"), aes(x=VitalRate, y=value))+
  geom_bar(stat="identity", position="dodge", fill="grey30")+
  ylab("Contribution of Climate Effects")+
  xlab("Vital Rate")+
  ggtitle("Individual level")+
  scale_y_continuous(limits=c(0, 0.5))+
  scale_x_discrete(labels=c("Recruitment", "Growth", "Survival"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
gClimCont2 <- ggplot(data=subset(plotD, Level=="Quadrat"), aes(x=VitalRate, y=value))+
  geom_bar(stat="identity", position="dodge", fill="grey30")+
  ylab("Contribution of Climate Effects")+
  xlab("Vital Rate")+
  ggtitle("Quadrat level")+
  scale_y_continuous(limits=c(0, 0.5))+
  scale_x_discrete(labels=c("Colonization", "Cover change", "Extirpation"))+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 25, hjust = 1))
library(gridExtra)
gClim <- grid.arrange(gClimCont1, gClimCont2, ncol=2, nrow=1)
gClim

```{r figure_S2, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
gQC <- read.csv("../montana/quadBM/vitalRateRegressions/growth/growthQuants.csv")
gQC <- gQC[137:152,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gQC$X <- rep(coefNames, each=4)
gQC$rate <- "growth"
sQC <- read.csv("../montana/quadBM/vitalRateRegressions/survival/survivalQuants.csv")
sQC <- sQC[33:48,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sQC$X <- rep(coefNames, each=4)
sQC$rate <- "survival"
rQC <- read.csv("../montana/quadBM/vitalRateRegressions/colonization/colonizationQuants.csv")
rQC <- rQC[29:44,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rQC$X <- rep(coefNames, each=4)
rQC$rate <- "colonization"
plotQC <- rbind(gQC,sQC,rQC)
gQ <- ggplot(plotQC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"))+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[133:148,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[81:96,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X ~ .)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"),
                     labels=c("recruitment", "growth", "survival"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Individual level")

####
#### Plot just for growth
####
growthIC <- subset(plotIC, rate=="growth")
growthQC <- subset(plotQC, rate=="growth")
growthIC$Level <- "Individual"
growthQC$Level <- "Quadrat"
growthAll <- rbind(growthIC, growthQC)

gGrowth <- ggplot(growthAll, aes(x=species, y=X50., color=Level))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "slateblue"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")
# print(gGrowth)

>>>>

```{r figure_S1, dependson="plot-options", fig.cap="Posterior means (vertical ticks), 75% credible intervals (heavy lines), and 95% credible intervals (light lines) of climate effects on growth at both levels of inferences. The dashed vertical line is at 0, indicating no effect.", fig.width=8, fig.height=7, cache=FALSE, results='hide'}
qbm_quants <- read.csv("../montana/quadBM/vitalRateRegressions/truncNormModel/growthQuants.csv")
qbm_quants <- qbm_quants[137:156,]
qbm_quants <- qbm_quants[-c(9:12),]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
qbm_quants$X <- rep(coefNames, each=4)
gQ <- ggplot(qbm_quants, aes(x=species, y=X50., group=species), color="grey25")+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X~.)+
  coord_flip()+
  theme_bw()+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Quadrat level")

gIC <- read.csv("../montana/ipm/vitalRateRegs/growth/growthQuants.csv")
gIC <- gIC[141:156,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
gIC$X <- rep(coefNames, each=4)
gIC$rate <- "growth"
sIC <- read.csv("../montana/ipm/vitalRateRegs/survival/survivalQuants.csv")
sIC <- sIC[141:156,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
sIC$X <- rep(coefNames, each=4)
sIC$rate <- "survival"
rIC <- read.csv("../montana/ipm/vitalRateRegs/recruitment/recruitmentQuants.csv")
rIC <- rIC[85:100,]
coefNames <- c("ppt1", "ppt2", "temp1", "temp2")
rIC$X <- rep(coefNames, each=4)
rIC$rate <- "colonization"
plotIC <- rbind(gIC,sIC,rIC)
gI <- ggplot(plotIC, aes(x=species, y=X50., color=rate))+
  geom_hline(aes(yintercept=0), linetype="dashed")+
  geom_errorbar(aes(ymin=X2.5., ymax=X97.5.), width=0, position=position_dodge(width=0.5))+
  geom_errorbar(aes(ymin=X25., ymax=X75.), width=0, size=1.25, position=position_dodge(width=0.5))+
  geom_point(size=4, position=position_dodge(width=0.5), shape="|")+
  ylab("Standardized Coefficient Value")+
  xlab("Species")+
  facet_grid(X ~ .)+
  coord_flip()+
  theme_bw()+
  scale_color_manual(values=c("grey25", "steelblue", "slateblue"),
                     labels=c("recruitment", "growth", "survival"))+
#   guides(color=FALSE)+
  guides(color=guide_legend(title=""))+
  theme(legend.position="top")+
  ggtitle("Individual level")

### 2015-03-05 manuscript/suppMat.tex
updated figures

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S1.pdf}
\caption{The proportion of interannual variability in vital rates
explained by the climate covariates. The contribution for growth is
defined as: (Climate model - Constant Model)/(Full model - Constant
model). The contribution for survival and colonization, where we could
not estimate a full model with year random effects at the quadrat level,
is defined as: (Constant Model - Climate Model)/Constant Model.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S2.pdf}
\caption{Posterior means (vertical ticks), 75\% credible intervals
(heavy lines), and 95\% credible intervals (light lines) of climate
effects on growth at both levels of inferences. The dashed vertical line
is at 0, indicating no effect.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{components/figure/manuscript-figure_S1.pdf}
\caption{Posterior means (vertical ticks), 75\% credible intervals
(heavy lines), and 95\% credible intervals (light lines) of climate
effects on growth at both levels of inferences. The dashed vertical line
is at 0, indicating no effect.}
\end{figure}
